Weather covariance matrices as U_hyp for GR50

### 2021-01-23 R/Analysis_v0.6_weather_covariance_Uhyp_greenup.Rmd
Finish mash hypothesis-driven covariance matrix Results section

```{r}
annos_gg %>%
  filter(cgdd_12c_18d_Gulf_and_Midwest.10 > 0.05 |
           tave_18d_Gulf_and_Midwest.6 > 0.05) %>%
  dplyr::select(where(not_all_na))

annos_gamg %>%
  filter(cgdd_12c_18d_Gulf_and_Midwest.10 > 0.05 |
           cgdd_12c_18d_Gulf_and_Midwest.9 > 0.05) %>%
  dplyr::select(where(not_all_na))

annos_gamf %>%
  # dplyr::select(starts_with("dyln_change_sec"))
  filter(dyln_change_sec_Midwest.7 > 0.05) %>%
  dplyr::select(where(not_all_na))
annos_mf %>%
  # dplyr::select(starts_with("cgdd_12c_gr2fl_Gulf_and"))
  filter(cgdd_12c_gr2fl_Gulf_and_Midwest.8 > 0.05) %>%
  dplyr::select(where(not_all_na))
```
Not many SNPs with U_hyp loading > 10% and SNP with log10BF > 2:
Both GR: 10 & 9 SNPs   cgdd_12c_18d_Gulf_and_Midwest x2 (0.9 and 0.10)
Both FL: 2 SNPs        dyln_change_sec_Midwest.7

>>>>

```{r}
annos_gg %>%
  filter(cgdd_12c_18d_Gulf_and_Midwest.10 > 0.1 |
           tave_18d_Gulf_and_Midwest.6 > 0.1) %>%
  dplyr::select(where(not_all_na))

annos_gamg %>%
  filter(cgdd_12c_18d_Gulf_and_Midwest.10 > 0.1 |
           cgdd_12c_18d_Gulf_and_Midwest.9 > 0.1) %>%
  dplyr::select(where(not_all_na))

annos_mf %>%
  # dplyr::select(starts_with("cgdd_12c_gr2fl_Gulf_and"))
  filter(cgdd_12c_gr2fl_Gulf_and_Midwest.8 > 0.1) %>%
  dplyr::select(where(not_all_na))
annos_gamf %>%
  # dplyr::select(starts_with("dyln_change_sec"))
  filter(dyln_change_sec_Midwest.7 > 0.1) %>%
  dplyr::select(where(not_all_na))
